Assessing Gender Bias in Machine Translation

### 2017-12-15 paper/main.tex
Updates on paper

\usepackage{multirow}
\usepackage{hyperref}
\usepackage{float}
\usepackage{array}
\usepackage{dirtytalk}
\usepackage{csquotes}
\usepackage{amsmath}
\usepackage{graphicx}
%
%
%\usepackage{xltxtra}

@@

We believe that the phenomenon of gender bias in machine translation can be assessed by mapping sentences constructed in gender neutral languages to English by the means of an automated translation tool. Specifically, we can translate sentences such as the Hungarian \say{ő ápolónő}, where \say{ápolónő} translates to \say{nurse} and \say{ő} is a gender-neutral pronoun meaning either he, she or it, to English, yielding in this example the result \say{she's a nurse} in Google Translate. The same basic template can be ported to all other gender neutral languages, as Table \ref{tab:templates} shows. Given the success of Google Translate, which amounts to 200 million users daily, we have decided to exploit its API to obtain the desired thermometer of gender bias. Also, in order to solidify our results, we have decided to work with as many gender neutral languages as possible, obtaining a list of these from the Wikipedia article \url{https://en.wikipedia.org/wiki/Gender_neutrality_in_genderless_languages}. Table \ref{tab:gender-neutral-languages} compiles all languages from said article, with additional columns informing whether they 1) exhibit a pronominal gender system and 2) are supported by Google Translate. Because pronominal gender systems defy the purposes of our technique, such languages have been discarded.

There is a prohibitively large class of nouns and adjectives that could in principle be substituted in the templates of Table \ref{tab:templates}. To simplify our dataset, we have decided to obtain a comprehensive list of professional occupations, which, we believe, are an interesting window into the nature of gender bias. Once again we resorted to a Wikipedia article (\url{https://en.wikipedia.org/wiki/Lists_of_occupations}) to collect this data, of which the statistics of occupations per category (Artistic, Corporate, Theatre, etc.) is shown in Table \ref{tab:occupations}. Finally, Table \ref{tab:occupations-examples} shows thirty examples of randomly selected occupations from our dataset.

\begin{table}[H]
	\centering
	\begin{tabular}{|c|c|m{3cm}|c|}
	\hline
	Language Family & Language & Pronominal Gender System & Supported \\ \hline \hline
	\multirow{2}{*}{Austronesian} & Malay & No & Yes \\
	& Tagalog & No & \textbf{No} \\ \hline
	\multirow{3}{*}{Finno-Ugric} & Estonian & No & Yes \\
	& Finnish & No & Yes\\
	& Hungarian & No & Yes \\ \hline
	\multirow{4}{*}{Indo-European} & Armenian & No & Yes \\
	& Bengali & No & Yes \\
	& English & \textbf{Yes} & Yes \\{}
	& Persian & \textbf{Yes} & Yes \\ \hline
	\multirow{3}{*}{Indo-Aryan} & Maithili & No & \textbf{No} \\
	& Nepali & No & Yes \\
	& Oriya & No & \textbf{No} \\ \hline
	\multirow{10}{*}{} & Japanese & No & Yes \\
	& Korean & \textbf{Optional} & Yes \\
	& Turkish & No & Yes \\
	& Yoruba & No & Yes \\
	& Basque & No & Yes \\
	& Swahili & No & Yes \\
	& Chinese & \textbf{Optional} & Yes \\
	& Cantonese & No & \textbf{No} \\
	& Pipil & No & \textbf{No} \\
	& Quechuan & No & \textbf{No} \\ \hline
	\multirow{4}{*}{Constructed} & Esperanto & \textbf{Yes} & Yes \\
	& Ido & \textbf{Optional} & \textbf{No} \\
	& Lingua Franca Nova & No & \textbf{No} \\
	& Interlingua & No & \textbf{No} \\ \hline
	\end{tabular}
	\label{tab:gender-neutral-languages}
	\caption{Selected gender neutral languages obtained from the Wikipedia article \url{https://en.wikipedia.org/wiki/Gender_neutrality_in_genderless_languages}. Languages are grouped according to language families and classified according to whether they exhibit pronominal gender system. For the purposes of this work, we have decided to work only with languages lacking such a system, and as such Persian and Esperanto have been discarded. Because Tagalog, Maithili, Oriya, Cantonese, Pipil, Quechuan, Lingua Franca Nova and Interlingua lack support from Google Translate, these languages have also been ommitted from this work.}
\end{table}

\begin{table}[H]
	\centering
	\begin{tabular}{|c|c|}
	\hline
	Category 		& \# Occupations 	\\ \hline \hline
	Artistic 		& $102$ 			\\ \hline
	Computer 		& $19$ 				\\ \hline
	Corporate 		& $50$ 				\\ \hline
	Dance 			& $9$ 				\\ \hline
	Film/Television & $26$ 				\\ \hline
	Healthcare 		& $88$ 				\\ \hline
	Industrial 		& $26$ 				\\ \hline
	Science 		& $50$ 				\\ \hline
	Service 		& $10$ 				\\ \hline
	Theatre 		& $52$ 				\\ \hline
	Writing 		& $29$ 				\\ \hline
	\hline
	Total			& $436$				\\ \hline
	\end{tabular}
	\label{tab:occupations}
	\caption{Selected occupations obtained from the Wikipedia article \url{https://en.wikipedia.org/wiki/Lists_of_occupations}, grouped by category. We have selected a total of $453$ occupations from $11$ distinct groups (Artistic, Science, Service, etc.).}
\end{table}

\begin{table}[H]
	\centering
	\begin{tabular}{|c|c|}
	\hline
	Language 	& Sentence template \\ \hline \hline
	Malay		& dia adalah $\langle occupation \rangle$ \\ \hline
	Estonian	& ta on $\langle occupation \rangle$ \\ \hline
	Finnish		& hän on $\langle occupation \rangle$ \\ \hline
	Hungarian	& ő $\langle occupation \rangle$ \\ \hline
	Armenian	& նա $\langle occupation \rangle$ է \\ \hline
	Japanese	& $\langle occupation \rangle$ です\\ \hline
	Turkish		& o bir $\langle occupation \rangle$ \\ \hline
	Yoruba		& o jẹ $\langle occupation \rangle$ \\ \hline
	Basque		& $\langle occupation \rangle$ da \\ \hline
	Swahili		& yeye ni $\langle occupation \rangle$ \\ \hline
	Chinese		& ta $\langle occupation \rangle$ \\ \hline
	\end{tabular}
	\label{tab:templates}
	\caption{Templates used to infer gender biases in the translation to the English language.}
\end{table}

\begin{table}[H]
	\centering
	\begin{tabular}{|c|c|c|c|c|}
	\hline
	stagehands & author & neurologist \\ \hline
	screenwriter & animator & marketing director \\ \hline
	biochemist & endocrinologist & freelancer \\ \hline
	neurosurgeon & computer scientist & petrochemical engineer \\ \hline
	food stylist & cardiothoracic surgeon & property master \\ \hline
	literary editor & video editor & animation director \\ \hline
	house manager & chief administrative officer & arts administration \\ \hline
	actor & dialysis technician & family nurse practitioner \\ \hline
	psychologist & chief creative officer & flash developer \\ \hline
	scenic artist & producer & medical laboratory scientist \\ \hline
	\end{tabular}
	\label{tab:occupations-examples}
	\caption{A randomly selected example subset of thirty occupations obtained from our dataset with a total of 436 different occupations.}
\end{table}

@@

\begin{table}[H]
	\centering
	\begin{tabular}{|c|c|c|c|c|c|}
	\hline
	Category & Female & Male & Neutral & Ratio & Total \\ \hline
	\hline
	Artistic        & 179    & 504  & 206     & 2.816 	& 918 \\ \hline
	Computer        & 7      & 125  & 39      & 17.857 	& 171 \\ \hline
	Corporate       & 36     & 340  & 74      & 9.444 	& 450 \\ \hline
	Dance           & 31     & 33   & 17      & 1.064 	& 81  \\ \hline
	Film-television & 54     & 125  & 55      & 2.315 	& 234 \\ \hline
	Healthcare      & 174    & 475  & 130     & 2.730 	& 792 \\ \hline
	Science         & 34     & 357  & 59      & 10.500 	& 450 \\ \hline
	Service         & 5      & 63   & 22      & 12.600 	& 90  \\ \hline
	Theatre         & 75     & 296  & 106     & 3.947 	& 477 \\ \hline
	Writing         & 41     & 148  & 72      & 3.610 	& 261 \\ \hline
	\hline
	Total           & 636    & 2466 & 780     & 3.877   &    \\ \hline
	\end{tabular}
	\label{tab:gender-by-category}
	\caption{Number of female, male and neutral pronominal genders per occupation category in the translated sentences. The corresponding sex ratios (\# Male / \# Female) show just how much male defaults are prominent in male dominated fields such as computer science, with up to $\approx 18$ occurrences of male pronouns for each of a female one.}
\end{table}

@@

\begin{table}[H]
	\centering
	\begin{tabular}{|c|c|c|c|c|c|}
	\hline
	Language & Female & Male & Neutral & Ratio & Total \\ \hline
	\hline
	Malay     & 43     & 392  & 0       & 9.116 	& 436   \\ \hline
	Estonian  & 121    & 309  & 0       & 2.554 	& 436   \\ \hline
	Finnish   & 167    & 263  & 0       & 1.575 	& 436   \\ \hline
	Hungarian & 174    & 255  & 2       & 1.465 	& 436   \\ \hline
	Armenian  & 94     & 337  & 1       & 3.585 	& 436   \\ \hline
	Japanese  & 2      & 207  & 222     & 103.500   & 436   \\ \hline
	Turkish   & 19     & 368  & 44      & 19.368 	& 436   \\ \hline
	Yoruba    & 11     & 290  & 131     & 26.364 	& 436   \\ \hline
	Basque    & 5      & 45   & 380     & 9.000		& 436   \\ \hline
	Swahili   & 68     & 363  & 0       & 5.338 	& 436   \\ \hline
	Chinese   & 13     & 359  & 58      & 27.615 	& 436   \\ \hline
	\hline
	Total 	  & 717    & 3188 & 838     & 4.446     &   \\ \hline
	\end{tabular}
	\label{tab:gender-by-category}
	\caption{Number of female, male and neutral pronominal genders per language in the translated sentences. The corresponding sex ratios (\# Male / \# Female) show just how much male defaults are prominent in some languages such as Chinese, with almost 30 male pronouns for each female one.}
\end{table}

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{pictures/gender-by-language}
	\label{fig:gender-by-language}
	\caption{The distribution of pronominal genders per language also suggests a tendency towards male defaults, with female pronouns reaching as low as $0.46\%$ and $2.98\%$ for Japanese and Chinese respectively. Some languages such as Japanese (and particularly Basque) were observed to yield a high number of neutral pronouns, but that is the exception rather than the rule among the tested idioms. Once again not all bars add up to $100\%$ as Google Translate occasionally fails to translate sentences.}
\end{figure}

>>>>

\usepackage{multirow}
\usepackage{hyperref}
\usepackage{float}
\usepackage{array}
\usepackage{dirtytalk}
\usepackage{csquotes}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{pifont}

\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{53}}%

@@

We believe that the phenomenon of gender bias in machine translation can be assessed by mapping sentences constructed in gender neutral languages to English by the means of an automated translation tool. Specifically, we can translate sentences such as the Hungarian \say{ő ápolónő}, where \say{ápolónő} translates to \say{nurse} and \say{ő} is a gender-neutral pronoun meaning either he, she or it, to English, yielding in this example the result \say{she's a nurse} on Google Translate. The same basic template can be ported to all other gender neutral languages, as Table \ref{tab:templates} shows. Given the success of Google Translate, which amounts to 200 million users daily, we have decided to exploit its API to obtain the desired thermometer of gender bias. Also, in order to solidify our results, we have decided to work with as many gender neutral languages as possible, obtaining a list of these from the Wikipedia article on the issue (\url{https://en.wikipedia.org/wiki/Gender_neutrality_in_genderless_languages}). Table \ref{tab:gender-neutral-languages} compiles all languages from said article, with additional columns informing whether they 1) exhibit a pronominal gender system and 2) are supported by Google Translate. Because pronominal gender systems defy the purposes of our technique, such languages have been discarded. Following difficulties with Bengali, Nepali and Korean we have decided not to work with these languages also.

There is a prohibitively large class of nouns and adjectives that could in principle be substituted in the templates of Table \ref{tab:templates}. To simplify our dataset, we have decided to obtain a comprehensive list of professional occupations, which, we believe, are an interesting window into the nature of gender bias. Once again we resorted to a Wikipedia article (\url{https://en.wikipedia.org/wiki/Lists_of_occupations}) to collect this data, of which the statistics of occupations per category (Artistic, Corporate, Theatre, etc.) are shown in Table \ref{tab:occupations}. Finally, Table \ref{tab:occupations-examples} shows thirty examples of randomly selected occupations from our dataset.

\begin{table}[H]
	\centering
	\begin{tabular}{|c|m{2cm}|m{2cm}|c|c|}
	\hline
	Language Family & Language & Pronominal Gender System & Supported & Tested \\ \hline \hline
	\multirow{2}{*}{Austronesian} 	& Malay 				& \xmark 			& \checkmark	& \checkmark	\\
									& Tagalog 				& \xmark 			& \xmark		& \xmark		\\ \hline
	\multirow{3}{*}{Finno-Ugric} 	& Estonian 				& \xmark 			& \checkmark 	& \checkmark	\\
									& Finnish 				& \xmark 			& \checkmark	& \checkmark	\\
									& Hungarian 			& \xmark 			& \checkmark 	& \checkmark	\\ \hline
	\multirow{4}{*}{Indo-European} 	& Armenian 				& \xmark 			& \checkmark 	& \checkmark	\\
									& Bengali 				& \xmark 			& \checkmark 	& \xmark		\\
									& English 				& \checkmark 		& \checkmark 	& \xmark 		\\
									& Persian 				& \checkmark 		& \checkmark 	& \xmark 		\\ \hline
	\multirow{3}{*}{Indo-Aryan} 	& Maithili 				& \xmark 			& \xmark 		& \xmark 		\\
									& Nepali 				& \xmark 			& \checkmark	& \xmark		\\
									& Oriya 				& \xmark 			& \xmark 		& \xmark 		\\ \hline
	\multirow{10}{*}{} 				& Japanese 				& \xmark 			& \checkmark 	& \checkmark	\\
									& Korean 				& O 				& \checkmark 	& \xmark		\\
									& Turkish 				& \xmark 			& \checkmark 	& \checkmark	\\
									& Yoruba 				& \xmark 			& \checkmark 	& \checkmark	\\
									& Basque 				& \xmark 			& \checkmark 	& \checkmark	\\
									& Swahili 				& \xmark 			& \checkmark 	& \checkmark	\\
									& Chinese 				& O 				& \checkmark 	& \checkmark	\\
									& Cantonese 			& \xmark 			& \xmark		& \xmark		\\
									& Pipil 				& \xmark 			& \xmark		& \xmark		\\
									& Quechuan 				& \xmark 			& \xmark		& \xmark		\\ \hline
	\multirow{4}{*}{Constructed} 	& Esperanto 			& \checkmark 		& \checkmark 	& \xmark		\\
									& Ido 					& O 				& \xmark 		& \xmark 		\\
									\cline{2-2}
									& Lingua Franca Nova 	& \xmark 			& \xmark 		& \xmark 		\\
									\cline{2-2}
									& Interlingua 			& \xmark 			& \xmark 		& \xmark 		\\ \hline
	\end{tabular}
	\caption{Selected gender neutral languages obtained from the Wikipedia article \url{https://en.wikipedia.org/wiki/Gender_neutrality_in_genderless_languages}. Languages are grouped according to language families and classified according to whether they exhibit pronominal gender system (\checkmark: yes, \xmark:~no, O: it is optional). For the purposes of this work, we have decided to work only with languages lacking such a system, and as such Persian and Esperanto have been discarded. Languages lacking support from Google Translate have been discarded. Following difficulties with Bengali, Nepali and Korean, these languages have also been discarded.}
	\label{tab:gender-neutral-languages}
\end{table}

\begin{table}[H]
	\centering
	\begin{tabular}{|c|c|}
	\hline
	Category 		& \# Occupations 	\\ \hline \hline
	Artistic 		& $102$ 			\\ \hline
	Computer 		& $19$ 				\\ \hline
	Corporate 		& $50$ 				\\ \hline
	Dance 			& $9$ 				\\ \hline
	Film/Television & $26$ 				\\ \hline
	Healthcare 		& $88$ 				\\ \hline
	Industrial 		& $26$ 				\\ \hline
	Science 		& $50$ 				\\ \hline
	Service 		& $10$ 				\\ \hline
	Theatre 		& $52$ 				\\ \hline
	Writing 		& $29$ 				\\ \hline
	\hline
	Total			& $462$				\\ \hline
	\end{tabular}
	\caption{Selected occupations obtained from the Wikipedia article \url{https://en.wikipedia.org/wiki/Lists_of_occupations}, grouped by category. We have selected a total of 462 occupations from $11$ distinct groups (Artistic, Science, Service, etc.).}
	\label{tab:occupations}
\end{table}

\begin{table}[H]
	\centering
	\begin{tabular}{|c|c|}
	\hline
	Language 	& Sentence template \\ \hline \hline
	Malay		& dia adalah $\langle occupation \rangle$ \\ \hline
	Estonian	& ta on $\langle occupation \rangle$ \\ \hline
	Finnish		& hän on $\langle occupation \rangle$ \\ \hline
	Hungarian	& ő $\langle occupation \rangle$ \\ \hline
	Armenian	& նա $\langle occupation \rangle$ է \\ \hline
	Japanese	& $\langle occupation \rangle$ です\\ \hline
	Turkish		& o bir $\langle occupation \rangle$ \\ \hline
	Yoruba		& o jẹ $\langle occupation \rangle$ \\ \hline
	Basque		& $\langle occupation \rangle$ da \\ \hline
	Swahili		& yeye ni $\langle occupation \rangle$ \\ \hline
	Chinese		& ta $\langle occupation \rangle$ \\ \hline
	\end{tabular}
	\caption{Templates used to infer gender biases in the translation to the English language.}
	\label{tab:templates}
\end{table}

\begin{table}[H]
	\centering
	\begin{tabular}{|c|c|c|c|c|}
	\hline
	stagehands & author & neurologist \\ \hline
	screenwriter & animator & marketing director \\ \hline
	biochemist & endocrinologist & freelancer \\ \hline
	neurosurgeon & computer scientist & petrochemical engineer \\ \hline
	food stylist & cardiothoracic surgeon & property master \\ \hline
	literary editor & video editor & animation director \\ \hline
	house manager & chief administrative officer & arts administration \\ \hline
	actor & dialysis technician & family nurse practitioner \\ \hline
	psychologist & chief creative officer & flash developer \\ \hline
	scenic artist & producer & medical laboratory scientist \\ \hline
	\end{tabular}
	\caption{A randomly selected example subset of thirty occupations obtained from our dataset with a total of 462 different occupations.}
	\label{tab:occupations-examples}
\end{table}

@@

For each one of the tested 462 occupations (see Tables \ref{tab:occupations}, \ref{tab:occupations-examples}), we used the Python Google Translate API (\url{http://py-googletrans.readthedocs.io/en/latest/}) to translate sentences built with the templates in Table \ref{tab:templates} from each one of the tested languages in Table \ref{tab:gender-neutral-languages} to English. The resulting sentences are then classified as \emph{female}, \emph{male} or \emph{neutral} according to their respective pronouns. Sentences starting with \say{She/She's/Her} are classified as female, sentences starting with \say{He/He's/His} are classified as male and sentences starting with \say{It/It's/Its/They/They're/Their} are classified as (gender) neutral. The results from this analysis, which can be found in \url{https://github.com/marceloprates/Gender-Bias}, are further discussed below.

One can see either in Table \ref{tab:gender-by-category} or Figure \ref{fig:gender-by-category} that not only does Google Translate exhibit a tendency towards male defaults, but also that this tendency is further enhanced for typically male dominated fields such as computer science (with a ratio of $17.857$ male pronouns per female pronoun). Sentences about occupations from the \emph{Corporate} and \emph{Science} category are also disproportionately translated with male pronouns (sex ratios $9.444$ and $10.5$ respectively), while those containing occupations from the \emph{Dance} category achieve a sex ratio of almost one ($1.064$). Not one category has achieved a balanced sex ratio, neither does any category exhibit more gender neutral than male pronouns. In total, female pronouns add up to $16.522\%$ among all categories, while male pronouns add up to $63.083\%$ and gender neutral pronouns to just $7.912\%$, yielding an average sex ratio of $3.818$.

\begin{table}[H]
	\centering
	\begin{tabular}{|c|c|c|c|c|c|}
	\hline
	Category & Female & Male & Neutral & Ratio & Total \\ \hline
	\hline
	Artistic        & 188 & 518 & 72 & 2.755 	& 918 \\ \hline
	Computer        & 7   & 125 & 12 & 17.857 	& 171 \\ \hline
	Corporate       & 36  & 340 & 23 & 9.444 	& 450 \\ \hline
	Dance           & 31  & 33  & 8  & 1.064 	& 81  \\ \hline
	Film-television & 54  & 125 & 18 & 2.315 	& 234 \\ \hline
	Healthcare      & 176 & 483 & 64 & 2.744 	& 792 \\ \hline
	Industrial      & 40  & 135 & 29 & 3.375   	& 234 \\ \hline
	Science         & 34  & 357 & 25 & 10.500	& 450 \\ \hline
	Service         & 5   & 63  & 10 & 12.600	& 90  \\ \hline
	Theatre         & 75  & 296 & 38 & 3.947 	& 477 \\ \hline
	Writing         & 41  & 148 & 30 & 3.610 	& 261 \\ \hline
	\hline
	Total           & 687 & 2623 & 329 & 3.818 & 4158 \\ \hline
	\end{tabular}
	\label{tab:gender-by-category}
	\caption{Number of female, male and neutral pronominal genders per occupation category in the translated sentences. The corresponding sex ratios (\# Male / \# Female) show just how much male defaults are prominent in male dominated fields such as computer science, with up to $\approx 18$ occurrences of male pronouns for each of a female one.}
\end{table}

@@

While grouping translations by category helps shed light on the stereotypical gender roles among different professions, grouping translations by language can help us understand the effect each different culture has on this issue. Table \ref{tab:gender-by-language} for instance shows some sex ratios even larger than the previous ones, particularly when translating from Yoruba ($25.333$), Chinese ($27.5$) and Japanese, the last one peaking at an impressive ratio of $107.5$ male per female pronouns. Figure \ref{fig:gender-by-language} shows that, when grouping by language, gender neutral pronouns can be more prominent than male pronouns at least in one case: translating sentences from Basque yields 153 neutral vs 50 male and 5 female pronouns. Unfortunately this is the exception rather than the rule, with Yoruba following after with 131 neutral vs 304 male and 12 female pronouns. In total, female pronouns add up to $18.687\%$ among all categories, while male pronouns add up to $81.626\%$ and gender neutral pronouns to $8.466\%$, yielding an average sex ratio of $4.368$ ($14.405\%$ larger than what we get from grouping among categories). It should be noted however that Japanese and Basque, the two languages which stood out from the behavior observed in Figure \ref{fig:gender-by-category}, are precisely the two that Google Translate found hardest to translate. These findings should, as a result, be taken with a grain of salt.

\begin{table}[H]
	\centering
	\begin{tabular}{|c|c|c|c|c|c|}
	\hline
	Language & Female & Male & Neutral & Ratio & Total \\ \hline
	\hline
	Malay     & 47  & 415  & 0   & 8.830 	& 462 \\ \hline
	Estonian  & 130 & 332  & 0   & 2.554 	& 462 \\ \hline
	Finnish   & 179 & 283  & 0   & 1.581 	& 462 \\ \hline
	Hungarian & 189 & 270  & 1   & 1.429 	& 462 \\ \hline
	Armenian  & 101 & 360  & 1   & 3.564 	& 462 \\ \hline
	Japanese  & 2   & 215  & 0   & 107.500  & 462 \\ \hline
	Turkish   & 22  & 394  & 43  & 17.909	& 462 \\ \hline
	Yoruba    & 12  & 304  & 131 & 25.333	& 462 \\ \hline
	Basque    & 5   & 50   & 153 & 10.000   & 462 \\ \hline
	Swahili   & 76  & 386  & 0   & 5.079 	& 462 \\ \hline
	Chinese   & 14  & 385  & 23  & 27.500   & 462 \\ \hline
	\hline
	Total     & 777 & 3394 & 352 & 4.368	& 4158   \\ \hline
	\end{tabular}
	\caption{Number of female, male and neutral pronominal genders per language in the translated sentences. The corresponding sex ratios (\# Male / \# Female) show just how much male defaults are prominent in some languages such as Chinese, with almost 30 male pronouns for each female one.}
	\label{tab:gender-by-language}
\end{table}

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{pictures/gender-by-language}
	\label{fig:gender-by-language}
	\caption{The distribution of pronominal genders per language also suggests a tendency towards male defaults, with female pronouns reaching as low as $0.46\%$ and $2.98\%$ for Japanese and Chinese respectively. Once again not all bars add up to $100\%$ as Google Translate occasionally fails to translate sentences, particularly in Japanese and Basque. Among all tested languages, Basque was the only one to yield more gender neutral than male pronouns.}
\end{figure}

Instead of grouping sentences either by category or language, we can also visualize each of them individually on a scatter plot. Figure \ref{fig:scatterplot-languages} shows each occupation as a point on a bi-dimensional lattice, arranged horizontally by their sex ratio and vertically by the proportion of gender neutral pronouns, both averaged over translations from all tested languages. Each point is also color coded according to that occupation's respective category (Artistic, Writing, Science, etc.).
